---
title: IDS ManyBabies and MA merged dataset
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: false
    code_folding: hide
---
  
  
```{r setup, include = F}
# load packages
library(tidyverse) 
library(knitr)
library(here)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, tidy = F,  cache = F, fig.height = 4)
theme_set(theme_classic())

``` 

```{r}
COMBINED_DATASET <- here("data/mb_ma_combined.csv")

full_dataset <- read_csv(COMBINED_DATASET)
```

Here's what the merged dataset looks like: 
```{r}
DT::datatable(full_dataset)
```


There are 76 MA effect sizes and 150 MB effect sizes. 

I left several of the methodological variables blank for the MB data right now, with the hope that someone with more experience (Jessica?) with the MB dataset could help fill them in. Those variables are:

  * num_trials
  * participant_design
  * presentation
  * response_mode 
  * setting 
  * speaker 
  * speaker_experience 
  * speaker_fam 
  * speaker_female 
  * speech_type 
  * test_lang
  
Explanations for these variables should be [here](https://github.com/langcog/metalab2/blob/master/metadata/spec.yaml).

Jessica filled in these variables (all except test_lang because I want to check with the group.)

Above link did not work, but I used the MB Meta-Analysis codebook to code the variables, available [here](https://docs.google.com/spreadsheets/d/1E2eGPYfTPlpbJZveSrJe6H3uf4KV1TbCClzAacMs_uo/edit#gid=1387133600)
  
There were also a couple variables from the MB data that I thought we could code in the MA data if we were so inclined:

  * parent_education
  * prop_caregiver_seat
  
  
  
 
